Methods for Large Scale Learning to Rank

### 2014-02-27 report/BenchmarkResults.tex
bagboo

Although the winning \ac{GBDT} models performs very well in terms of \ac{nDCG} their high complexity makes them unsuitable to use in production. The winning models take weeks to train and are very slow during query evaluation.

\chapter{Yandex Internet Mathematics competition}

\section{Results}

>>>>

Although the winning \ac{GBDT} models performs very well in terms of \ac{nDCG} their high complexity makes them unsuitable to use in production. The winning models take weeks to train and are very slow during query evaluation. An exception in training time is the BagBoo\cite{Pavlov2010} method used by Pavlov \& Brunk. The bagging component of the BagBoo method enables it to achieve high scalability through parallelism. Pavlov et al \cite{Pavlov2010} managed to train half a million trees on 200 nodes in 2 hours.
\chapter{Yandex Internet Mathematics competition}

\section{Results}
The Yandex Internet Mathematics competition was won by

### 2014-02-27 report/RelatedWork.tex
bagboo

The defined search query resulted in 3300 documents.

@@

>>>>

The defined search query resulted in 3300 documents. We evaluate the first 300 search results.

@@

\section{BagBoo: A hybrid Bagging-the-Boosting Model}
Pavlov et al\cite{Pavlov2010} at Yandex developed a hybrid model that combines two methods from ensemble learning: bagging and boosting. Bagging is a ensemble learning method in which $m$ training sets $D_1..D_m$ are constructed from the training set $D$ by uniformly sampling data items from $D$ with replacement. The bagging method is parallelisable by training each $D_i$ with $i \in \{1..m\}$ on a different node. Boosting is an ensemble learning method in which multiple weak learners are iteratively added together into one ensemble model in such a way that new models focus more on those data instances that were misclassified before. Boosting is not parallelisable, but the authors state that learning a short boosted sequence on a single node is still a do-able task.
